% the acknowledgments section

I have been a member of the Harvard ATLAS group for many years now, first as an undergraduate and then as a graduate student. As a result, I have had the privilege of interacting with many amazing people there over the years and have accumulated a large list of folks to thank. 

First and foremost, I must thank the two people who have effectively been my academic parents since I started in the Harvard group: Jo\~{a}o Guimar\~{a}es da Costa and Melissa Franklin. Melissa Franklin and Jo\~{a}o Guimar\~{a}es da Costa. They have both been so important to both my academic and personal development that I can't even put one before the other. Jo\~{a}o has been an excellent PhD advisor, showing me how to look at the big picture and helping me navigate the sometimes complicated politics of ATLAS. He got me started on my first projects with ATLAS as a young college sophomore before there was even beam in the LHC (go cosmic ray muons!). He has also been a constant source of advice and support, even when we have been on different continents. Melissa gave me my start in HEP as a summer student on CDF and has been an unbelievable mentor throughout my time at Harvard. I still remember our weekly chalkboard particle physics lessons after that first summer. She also graciously took me on as a co-advisee after Jo\~{a}o moved on to his new position at IHEP. I am incredibly lucky to have had both of them as advisors. 

Another mentor who was essential to my development as a graduate student is Paolo Giromini. His uncanny knowledge and intuition about detectors is unmatched and I am very grataeful to have had the chance to work with him on the micromegas for the ATLAS New Small Wheel upgrade project. I owe essentially all my practical knowledge about detectors (and building things in general) to him. I also appreciated his unique sense of humor which made sometimes difficult tasks much easier to get through.

I am grateful to John Huth and Masahiro Morii for their helpful advice as the other professors in the Harvard ATLAS group as well. I especially thank John for helping me get started on the micromegas trigger project and being a great professor to TF particle physics for. Additionally I thank Howard Georgi for serving as my third committee member and offering me feedback throughout my graduate career. 

I also owe enormous thanks to Hugh Skottowe, the postdoc that I worked most closely with in my early years as a graduate student. He was always able to help me through complicated tasks in everything from writing code to understanding difficult physics concepts. I particularly enjoyed walking down to his office in Palfrey at random times and talking through whatever problem I was tackling on that day. 

Alex Tuna, the second postdoc that I worked closely with at Harvard, deserves great thanks as well. He helped me push through to the end of my graduate career and offered great advice along the way. 

Being at Harvard, I have seen an incredible array of graduate students graduate before me: Ben Smith, Verena Martinez Outschoorn, Srivas Prasad, Michael Kagan, Giovanni Zevi Della Porta, Laura Jeanty, Kevin Mercurio, William Spearman, and Andy Yen. I want to thank them all for showing me what a good physicist looks like and for patiently answering my questions and offering insightful advice about physics and life. 

Getting through graduate school would not have been possible without the support and friendship of the other students in our group. Thanks to Emma Tolley for geeking out with me about cool computing stuff, going to taste delicious beers with me, and helping start the Palfrey tradition of Taco Tuesdays. Thanks to Brian Clark for being a great friend and housing companion both in Kirkland House and in our tiny summer apartment in Geneva (and thanks to his partner Allison Goff for the same reasons!). Thanks to Siyuan Sun for giving me my first aikido lesson and always being there for great conversations, big and small. Tony (Baojia) Tong deserves special recognition for working with me on the $4b$ analysis and putting up with my sometimes strange requests (and giving me rides to the Val Thoiry Migros so I wouldn't have to pay exorbitant Geneva grocery prices!). Stephen Chan is probably the only student in the group who both understands my references to the Sopranos and makes some of his own. To the younger graduate students - Karri Di Petrillo, Jennifer Roloff, Julia Gonski, and Ann Wang - I want to say thank you for making the group a fun and lively place to be and giving all of us energy that the older graduate students like myself can sometimes lack. 

I'd like to thank Annie Wei and Gray Putnam, the two undergraduates I have worked with as a graduate student. Their unbelievable intuition and quickness in picking up difficult particle physics concepts is inspiring. 

I would also like to thank all of the postdocs that I have interacted with in my time in the Harvard group: Kevin Black, Alberto Belloni (who would always ask me ``Do you have it?"...I can now say that I do!), Shulamit Moed, Corrinne Mills, Geraldine Conti, David Lopez Mateos, Chris Rogan, Valerio Ippolito, and Stefano Zambito. 

There are many people on ATLAS who have helped me get to this point as well. In the $WW$ group, I have to thank Jonathan Long, Joana Machado Miguens, Ben Cerio, Philip Chang, Bonnie Chow, Richard Polifka, Heberth Torres, Tae Min Hong, and Jennifer Hsu for being wonderful colleagues and making the entire analysis run smoothly. In the $4b$ group, I have to thank Qi Zeng, Tony Tong, Alex Tuna, Michael Kagan, Max Bellomo, John Alison, and Patrick Bryant. 

Kirkland House was my home for the last three years of graduate school and was an wonderful environment and support system. I want to thank my fellow tutors, especially Brian Clark and Allison Goff (again), Zach Abel, Kelly Bodwin, Alex Lupsasca, John and Pam Park, Luke and Erin Walczewski, and Philip Gant for their friendship and support. I also want to thank Kate Drizos Cavell, Bob Butler, and the Faculty Deans Tom and Verena Conley.

There are still a few friends that haven't been covered yet and deserve great thanks. Jake Connors and Meredith MacGregor have been absolutely wonderful friends and I thank them in particular for the many home-cooked meals and great conversations we've had in their apartment. Nihar Shah has been my friend and confidant since we were both wee freshmen in Harvard Yard. Gareth Kafka, though he sits on the ``neutrino" side of Palfrey House, has made days there more fun and has also been an enthusiastic participant in the Palfrey Taco Tuesdays.  

Being at Harvard necessarily means having to navigate through bureaucracy at some point or another. I thank Lisa Cacciabaudo, Carol Davis, and Jacob Barandes for always having open doors and being the most kind, helpful people in the Physics department. 

I thank Venky Narayanamurti for putting on a great SPU course that I was proud to be a part of and TF for. I'd also like to thank Jim Waldo for offering me much advice about working in Computer Science and giving me a fun data project to be a part of in my free time. 

I grew up in a very tight knit Serbian community on the south side of Chicago which helped make me the person I am today. I would like to thank all of the people at St. Simeon Mirotochivi Serbian Orthodox Church who have always been sources of enthusiasm and support in my life. 

I would not be here without the unconditional love and constant support and encouragaement of my family. To my pokojni Dedas Branko and Miloje, my pokojni Baba Milka, and my Baba Desa, I want to say thank you for instilling in me at an early age the love of curiosity and storytelling that I have carried throughout my life. To my sister Angelina, I want to say thank you for always loving me and being my partner in crime throughout our childhoods. To my parents, Miroljub and Nada, Tata and Mama, I really cannot express how grateful I am to you and how much I owe you. As I look back now I see how I am a combination of both of your best qualities and every day I am in situations where I understand more and more the lessons you made sure to teach me and the sacrifices you made to make sure I got the best possible education. I love you all. 

Finally, I have to thank my soul mate, the one person in my life who understands me more than anyone else, my fiancee Kelly Brock. You are my sounding board, my support system, my cheerleader (figuratively and literally!), my best friend, my role model, and my everything. I would not have gotten through graduate school without you and my life would not be the same without you. I cannot wait to start our new lives together as the married doctors, tackling whatever comes our way with the same zeal with which we tackled graduate school. I love you with all my heart and soul. 

