\begin{savequote}[75mm]
The feeling is less like an ending than just another starting point.
\qauthor{Chuck Palahniuk}
\end{savequote}

\chapter{Combined Run 1 $H\rightarrow WW^{*}\rightarrow \ell\nu\ell\nu$ results}

\section{Introduction}

In the final statistical analysis of \HWWfull, the dedicated gluon-gluon fusion and vector boson fusion sensitive signal regions are all combined into a single fit to determine the main parameters of interest, the Higgs signal strength $\mu$ and mass $m_H$. Therefore, while the specific requirements applied for the VBF sensitive analysis are discussed in chapter 5, the final measurement of these parameters can only be discussed in combination with the results of the ggF dedicated analysis. For example, because ggF Higgs production is considered a background in the VBF analysis, the ggF dedicated signal regions can actually constrain the normalization of this background in the VBF dedicated region.

This chapter presents the combined interpretation of results in the \HWWfull analysis for gluon fusion and vector boson fusion Higgs production. First, the results of the dedicated gluon fusion search are presented. Then, a comparison of the individual production mode signal strengths ($\mu_{\ggF}$ and $\mu_{\VBF}$ and a measurement of the combined signal strength ($\mu$) are shown. Subsequently, the measured values of the Higgs couplings to fermions and vector bosons is presented. Finally, the cross section measurement for ggF and VBF production are shown. 

